\chapter{Introduction}
Handover is a key process in \ac{4G} cellular networks. It allows customers to be able to continue their calls and use services while moving out of range of the base station they are currently connected to by transferring the resources for that customer to another base station. The 4G network, \ac{LTE}, can make use of the automation paradigm known as a Self-organising network. One part of this paradigm, Self-optimisation, allows for the parameters used in the handover process to be optimised. In this project a reinforcement learning technique known as Q-Learning was used to carry out the optimisation of these parameters.

The performance of handovers within a cellular network is very important. Initiating a handover too late can cause an on-going call to be dropped by the network. This would be viewed as poor \ac{QoS} by the customer.  However, initiating a handover too early also comes with its own problems. It can cause handover ping-pongs where a mobile's connection switches back and forth between base stations in a short period of time and this wastes resources within the network.  

A simulation was created that would simulate mobile phones moving around a group of network base stations. This simulation would be used to determine the performance of the machine learning algorithm compared to if no optimisation was taking place. It would also supply the machine learning algorithm with rewards to indicate if it is making decisions that are beneficial or detrimental to the performance of the network.
\section{Project Objectives}\label{sec:obj}
The main objective of this project was to development a machine learning algorithm to fine tune the parameters used in the handover process of 4G networks.

Key Objectives:
\begin{itemize}
	\item Research and understand the parameters used in 4G handovers.
	\item Create a basic simulation of a 4G network with mobiles moving around a group of base stations.
	\item Implement a machine learning algorithm to fine-tune the handover parameters to improve the performance of the network.
	\item Evaluate the success of the machine learning approach in 4G handovers and compare this to using static parameters.
\end{itemize}

The schedule for the project can be seen in Table~\ref{tab:sch}
\begin{table}[H]
  \begin{center}
    \begin{tabular}{| p{8cm} | p{5.5cm} |}
  	  \hline
      \textbf{Project Milestone} & \textbf{Expected Time of Completion Time} \\ \hline
      Basic Movement simulation. & Sem 1: Week 4 to Week 8  \\ \hline
      Research 4G system parameters for handovers and implement network functions into simulation. & Sem 1: Week 6 to Week 11 \\ \hline
      Implement machine learning algorithm for fine tuning of handovers. & Sem 2: Week 1 to Week 8 \\ \hline
      Writing final report. & Sem 1: Week 10 to Sem 2: Week 12  \\ \hline
  	\end{tabular}
  \end{center}
  \caption{Basic schedule of the project.}
  \label{tab:sch}
\end{table}
\section{Project Outcomes}
During the course of the project it has been possible to meet all of the objectives. The parameters that are used in the handover process, the \ac{TTT} and \ac{hys}, were researched and the ways they are used were discovered. A basic simulation of a cellular network has been created and a Q-Learning algorithm was developed that optimised the handover parameters.

Experiments were run to find the worth of the machine learning system against using static values for the handover parameters. It was found that the machine learning system was able to improve the performance of the network. However, the system was found to have the potential to perform even better.   
\section{Dissertation Outline}
Chapter 2 describes a basic account of a 4G network along with the handover process. Chapter 3 gives a brief discussion on the different types of machine learning and goes more in-depth into reinforcement learning and Q-Learning. Chapter 4 describes the different propagation and mobility models considered for use within the simulation, as well as giving accounts of how the simulation was designed and the testing done to make sure the simulation was functioning as required. Chapter 5 describes the approach taken to the machine learning problem and the experiments run to find the worth of the system. This chapter also gives the results of the experiments and these results are discussed. Chapter 6 discusses the possible future work that could take this project further. Finally, Chapter 7 gives an account of the conclusions drawn from the project.